Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-28 paper-1/manuscript.tex
Added grand median comparisons to F7 stats

Inspecting the non-target response reduction in the full model in Figure \ref{fig7}b, we found that it was on average larger than in the ablated model (T = 4.16e+03, p = 0.0175; one-sided Wilcoxon, n = 120), if only by a small amount on the order of 0.03 spikes per neuron. Based on the ablated model analysis in Figure \ref{fig5}, we expected reduced non-target responses to similarly reduce the TA levels at the start of A trials. Indeed, the non-target response contrast remained tightly correlated with the contrast (dev - msc) in $V_{TA}$ at the start of target trials (median Pearson's $\rho$ = 0.989), as shown in Figure \ref{fig7}c. Correspondingly, $V_{TA}$ was reduced in dev, as shown in Figure \ref{fig7}d, and this too by a slighly greater amount in the full model than in the ablated model (T = 4.37e+03, p = 0.0257).

Finally, based on the ablated model analysis in Figure \ref{fig4}, we sought to confirm that lowered $V_{TA}$ before target trials was responsible for the increased target response. As shown in Figure \ref{fig7}e, the contrasts (dev - msc) in $V_{TA}$ at the start of target trials and in response magnitude to A were negatively correlated (T = 30, p = 2.09e-21, median = -0.268; one-sided Wilcoxon, n = 120), though the correlation was weaker in the full model (T = 1.67e+03, p = 1.49e-07). Despite the weaker correlation, however, the full model target response was clearly increased in dev over msc, and this increase was greater than in the ablated model (T = 1.94e+03, p = 0.000723), as shown in Figure \ref{fig7}f. This greater contrast, of course, directly reflects the greater DDI reported in Figure \ref{fig3}.

>>>>

Inspecting the non-target response reduction in the full model in Figure \ref{fig7}b, we found that it was on average larger than in the ablated model (T = 4.16e+03, p = 0.0175; one-sided Wilcoxon, n = 120), with the grand medians differing by 36\%. Based on the ablated model analysis in Figure \ref{fig5}, we expected reduced non-target responses to similarly reduce the TA levels at the start of A trials. Indeed, the non-target response contrast remained tightly correlated with the contrast (dev - msc) in $V_{TA}$ at the start of target trials (median Pearson's $\rho$ = 0.989), as shown in Figure \ref{fig7}c. Correspondingly, $V_{TA}$ was reduced in dev, as shown in Figure \ref{fig7}d, and this too by a slighly greater amount in the full model than in the ablated model (T = 4.37e+03, p = 0.0257).

Finally, based on the ablated model analysis in Figure \ref{fig4}, we sought to confirm that lowered $V_{TA}$ before target trials was responsible for the increased target response. As shown in Figure \ref{fig7}e, the contrasts (dev - msc) in $V_{TA}$ at the start of target trials and in response magnitude to A were negatively correlated (T = 30, p = 2.09e-21, median = -0.268; one-sided Wilcoxon, n = 120), though the correlation was weaker in the full model (T = 1.67e+03, p = 1.49e-07). Despite the weaker correlation, however, the full model target response was clearly increased in dev over msc, as shown in Figure \ref{fig7}f, and this increase was greater than in the ablated model (T = 1.94e+03, p = 0.000723), with the grand medians differing by 94\%. This greater contrast, of course, directly reflects the greater DDI reported in Figure \ref{fig3}.
